---
title: "tp-batman"
author: "Simon Biend"
date: "09/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(corrplot)
```

## R Markdown

```{r}
mydata <- read.csv("bats.csv", sep = ";", skip = 3, header =  T)
mydata$BRW <- mydata$BRW/1000
names(mydata)
```

## Study of the relationship between brain weight and body mass

```{r}
phyto = mydata[(mydata$Diet==1),]
ggplot(data = phyto, aes(x = BOW, y = BRW)) + geom_point()
```

```{r}
reg1 <- lm(BRW ~ BOW, data = phyto)
summary(reg1)
```
BRW  = 0.6234469 + 0.0089999 * BOW
BRW = a1 +  a2 * BOW

The estimate of the intercept is 623.4469, the p-value is less than 2e-16 for the slope and equal to 3.14e-08 for the intercept
H0 hypothesis says that a1 = a2 = 0, We can say the brain weight is linearly dependent of the body mass, the coefficient of determination is 0.95

```{r}
anova(reg1)
```
Additional information : the residuals and statistics  about the impact of BOW on BRW, the sum of residual is 4.4254



```{r}
plot(reg1$fitted.values, reg1$residuals, xlab = "Predicted", ylab = "Residuals")
```
```{r}
plot(reg1, 4)
```


```{r}
which(phyto$BRW>8)
```
```{r}
phytobis = phyto[which(phyto$BRW<8),]
```

```{r}
reg2 = lm(BRW ~ BOW, data = phytobis)
summary(reg2)
```
```{r}
par(mfcol = c(2, 2))
plot(reg1)
plot(reg2)
```
## Study of the contribution of the total weight of each part of the brain
```{r}
phytoNum <- phyto[, c(4:8)]
mat.cor = cor(phytoNum)
corrplot(mat.cor, type = "upper")
```
```{r}
cor.test(phyto$BRW, phyto$HIP)
cor.test(phyto$BRW, phyto$MOB)
cor.test(phyto$BRW, phyto$AUD)

```
We can conclude that the BRW is correlated with HIP, MOB and not with AUD

```{r}
regm = lm(BRW ~ AUD + MOB + HIP, data = phytobis)
summary(regm)
```
